manuscript_figures

### 2024-06-06 scripts/manuscript_figures.Rmd
map figure complete

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tigris)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(ggmap)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)
library(ggspatial)
if ("ggsn" %in% rownames(installed.packages()) == 'FALSE') BiocManager::install("ggsn")
library(ggsn)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
```

@@

# Define label data
labels <- data.frame(
  name = c("Narragansett\nBay", "Atlantic\nOcean"),
  lat = c(41.6, 41.3),
  lon = c(-71.35, -71.2)
)

# Plot
panelA <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_sf(data = site_rectangles, color = "red2", fill = NA, size = 2) + # Add rectangles around sites
  #geom_sf(data = sites_sf, color = "blue", size = 3) + # Add site points for reference
  geom_text(data = labels, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  coord_sf(xlim = c(-72, -71.0), ylim = c(41.1, 42.1), expand = FALSE) + # Zoom level
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.1, "in"), pad_y = unit(0.4, "in"),
                         style = north_arrow_fancy_orienteering) +
  theme_classic() # Remove axes and background

@@

# Define label data
labels <- data.frame(
  name = c("Fort\nWetherill"),
  lat = c(41.485),
  lon = c(-71.368)
)

# Plot
panelB <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_point(data = transect_fw,
             aes(x = Start.Longitude, y = Start.Latitude),
            color = "red", size = 3) + # Add start points of transects
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(1.5, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering) +
    geom_text(data = labels, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  theme_classic() + # Remove axes and background
  xlim(c(-71.45, -71.3)) + # Set longitude range
  ylim(c(41.42, 41.5))   # Set latitude range

@@

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tigris)
library(car)
library(MuMIn)
library(lmerTest)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(ggmap)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)
library(ggspatial)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)

@@

# Define label data
labels_tot <- data.frame(
  name = c("Narragansett\nBay", "Atlantic\nOcean"),
  lat = c(41.6, 41.3),
  lon = c(-71.35, -71.2)
)

# Plot panel A zoommed out RI and sites in rectangles
panelA <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_sf(data = site_rectangles, color = "red2", fill = NA, size = 2) + # Add rectangles around sites
  geom_text(data = labels_tot, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  coord_sf(xlim = c(-72, -71.0), ylim = c(41.1, 42.1), expand = FALSE) + # Zoom level
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(0.8, "in"), pad_y = unit(0.4, "in"),
                         style = north_arrow_fancy_orienteering) +
    # Change x and y axes names
  labs(x = "Longitude", y = "Latitude") +
  theme_classic() # Remove axes and background

@@

# Adjust latitude values by subtracting 0.0013
transect_fw <- transect_fw %>%
  mutate(
    Start.Latitude = Start.Latitude - 0.0013
  )

# Define label data
labels <- data.frame(
  name = c("Fort\nWetherill"),
  lat = c(41.486),
  lon = c(-71.368)
)

# Plot panel B for fort wetherill transects
panelB <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_point(data = transect_fw,
             aes(x = Start.Longitude, y = Start.Latitude),
             color = "black", fill = "red", size = 3, shape = 21) + # Add start points of transects
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(0.9, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering) +
    geom_text(data = labels, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  # Change x and y axes names
  labs(x = "Longitude", y = "Latitude") +
  theme_classic() + # Remove axes and background
  xlim(c(-71.45, -71.3)) + # Set longitude range
  ylim(c(41.42, 41.5))   # Set latitude range

@@

# Filter transect data by site
transect_kb <- filter(site, Site == "King's Beach")

# Define label data
labels_kb <- data.frame(
  name = c("King's\nBeach"),
  lat = c(41.463),
  lon = c(-71.33)
)

# Adjust latitude values by subtracting 0.0011
transect_kb <- transect_kb %>%
  mutate(
    Start.Latitude = Start.Latitude - 0.0001
  )

# Plot panel C for kings beach transects
panelC <- ggplot() +
  geom_sf(data = ri_state, fill = "lightgray") + # State boundaries
  geom_point(data = transect_kb,
             aes(x = Start.Longitude, y = Start.Latitude),
             color = "black", fill = "red", size = 3, shape = 21) + # Add start points of transects
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "bl", which_north = "true", 
                         pad_x = unit(0.8, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering) +
    geom_text(data = labels_kb, aes(x = lon, y = lat, label = name), size = 5, color = "black") + # Add labels
  # Change x and y axes names
  labs(x = "Longitude", y = "Latitude") +
  theme_classic() + # Remove axes and background
  xlim(c(-71.45, -71.3)) + # Set longitude range
  ylim(c(41.42, 41.5))   # Set latitude range

panelC

# Save the plot to a file
ggsave("output/figures/figure_1C.png", plot = panelC, width = 8, height = 6)

# Plot all three panels together using patchwork
```{r}

# Adjust width for individual plots
panelB <- panelB + theme(plot.margin = margin(r = 0))  # Remove right margin
panelC <- panelC + theme(plot.margin = margin(l = 0))  # Remove left margin

# Combine the plots with patchwork
combined_plot <- (panelA | (panelB / panelC)) +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 20, face = "bold"))

# Save the combined plot
ggsave("output/figures/figure_1.png", combined_plot, width = 10, height = 6, units = "in", dpi = 300)
